---
title: "assignment3_machine-learning-811223821"
author: "yada akhil"
date: "2022-10-06"
output:
  pdf_document: default
  word_document: default
---



#setting default values to get a clean output
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
```
#loading all the required packages.
```{r}
library(e1071)
library(ISLR)
library(caret)
library(FNN)
library(gmodels)

library(pivottabler)

library(reshape)

library(reshape2)

```
#reading the data as well as data partiton 
```{r }
UniversalBank <- read.csv("C:/Users/sudhakar/Downloads/UniversalBank (1).csv")

set.seed(15)


Index <- createDataPartition(UniversalBank$Income, p = 0.6, list = FALSE)

trainingData <- UniversalBank[Index,]

set.seed(15)


testData <- UniversalBank[-Index,]




```

# A.create a pivot for the training data with online as a column variable,CC as a row variabe, and loan as a secondary row variable.
```{r }
set.seed(15)
Melt_training = melt(trainingData,id=c("CreditCard","Personal.Loan"),variable= "Online")

cast_training=dcast(Melt_training,CreditCard+Personal.Loan~Online)
set.seed(15)
cast_training <-cast_training[c(1,2,14)]

cast_training
set.seed(15)

```
#b. Creation of pivot tables for the training data where one will loan (rows) as a function of online(columns)and the other will have loan (rows) as a function of CC (columns)

```{r}
set.seed(15)

Melt_training1 <- melt(trainingData,id=c("Personal.Loan"),variable = "Online")

cast_training1  <- dcast(Melt_training1,Personal.Loan~Online)

cast_training1 <-cast_training1[c(1,13)]

cast_training1

set.seed(15)

Melt_training2 <- melt(trainingData,id=c("CreditCard"),variable = "Online")

cast_training2 <- dcast(Melt_training2,CreditCard~Online)

cast_training2 <-cast_training2[c(1,14)]

cast_training2

```
#D.complete the following quantities p(A|B)
```{r}
set.seed(15)
trainingData1 <- trainingData[c(13,10,14)]



table(trainingData1[,c(3,2)])

#I) 84/(84+200) =  0.29577464788

#IV)  814/(814+1904) = 0.29948491537



table(trainingData1[,c(1,2)])

#II)  172/(112+172) = 0.60563380281

#V) 1610/(1610+1108) = 0.5923473142



table(trainingData1[,c(2)])

#III) 284/(284+2718) = 0.0946035976

#VI)  2718/(284+2693) = 0.91299966409

set.seed(15)
```
E. Use the quantities computed above to compute the naive Bayes probability P(Loan = 1 | CC = 1,
Online = 1).

```{r}
# calculation using above values as below

#0.29577464788 * 0.60563380281 * 0.0946035976/((0.0946035976 * 0.60563380281 * 0.29577464788) +( 0.91299966409 * 0.5923473142 * 0.29948491537))
```
#f. by comparing the value obtained by using teh navie bays probabilty the value obtained in step b 
#g.run the navie bayes model

```{r}
set.seed(15)

naivebayes = naiveBayes(Personal.Loan~.,data=trainingData1)

naivebayes

set.seed(15)
```
0.2957746 * 0.6056338 * 0.0946036 /((0.0946035976 * 0.60563380281 * 0.29577464788) +( 0.2994849 * 0.5923473 * 0.9053964 ))

which gives <b><i>0.09543910129</i></b>

<ins><b>Hence we can say that the results of naive bayes are similar to those of the previous methods i.e 0.09543910129 & which is the same as the previous response  0.09471959475 in E.).</b></ins>


